Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-02 neurips-20/cvx-flats.tex
Moving S6 things to appendix

In the proof of Theorem~\ref{thm:consistent-implies-indir-elic} below, we modify the argument of~\citet[Corollary 7]{frongillo2018elicitation} to bound the convex elicitation complexity of the Bayes risk of the loss.
\btw{Raf Note to self: need to sync the refs to the actual version on arxiv... or something...}
\begin{theorem}
  \label{thm:bayes-risk-lower-bound}
  Let $L$ elicit some $\Gamma:\simplex\to\reals^d$.
  Let $p\in\relint\simplex$ and let $\Gamma_r$ be some level set of $\Gamma$ such that
  (i) $p\in\Gamma_r$,
  (ii) $\codim(\affhull(\Gamma_r))=d$, and
  (iii) either $\Gamma_r$ is a singleton or $\lbar$ is nonconstant on $\Gamma_r$.
  Then $\eliccvx(\lbar) \geq \min(d+1,n-1)$.
\end{theorem}
\begin{proof}
  Suppose that we have some convex loss $\hat L:\reals^k\times\Y\to\reals$ eliciting a property $\hat\Gamma:\simplex\to\reals^k$, and link $\psi : \reals^k \to \reals$ such that $\lbar = \psi \circ \hat\Gamma$.
  % The condition $\iden(\Gamma)=d$ implies the existence of some level set $\Gamma_r$ such that $\codim(\affhull(\Gamma_r)) \geq d$; otherwise, taking $F_r = \affhull(\Gamma_r)$ for all reports $r\in\reals^d$, we would have $\codim(F_r) \leq d-1$ and $\Gamma_r = F_r \cap \simplex$, implying $\iden(\Gamma)\leq d-1$.
  The proof of \citet[Theorem 4]{frongillo2018elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that every level set of $\hat\Gamma$ is contained in a level set of $\Gamma$; for completeness we give the argument here.
  Suppose for a contradiction that we have $p,p'$ with $\hat\Gamma(p)=\hat\Gamma(p')$ but $\Gamma(p) \neq \Gamma(p')$.
  As $\lbar = \psi \circ \hat\Gamma$, we also have $\lbar(p) = \lbar(p')$.
  Letting $p'' = \tfrac 1 2 p +  \tfrac 1 2 p'$, Lemma~\ref{lem:elic-complex-bayes-concave} would then give us $\lbar(p'') >  \tfrac 1 2 \lbar(p) +  \tfrac 1 2 \lbar(p') = \lbar(p)$.
  By \citet{osband1985providing}, the level sets $\hat\Gamma_{\hat r}$ are convex, giving $\hat\Gamma(p'') = \hat\Gamma(p)$, which would imply $\lbar(p'')=\lbar(p)$, contradicting $\lbar = \psi \circ \hat\Gamma$.
  We conclude $\hat\Gamma$ must refine $\Gamma$, and thus $\hat L$ actually indirectly elicits $\Gamma$ through some other link function.
  % The proof of \cite[Theorem 4]{frongillo2018elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that for all $\hat r \in \hat\Gamma(\simplex)$ we have $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ for some $r\in\reals^k$.

@@

>>>>

In the proof of Theorem~\ref{thm:bayes-risk-lower-bound}\jessiet{??} below, we modify the argument of~\citet[Corollary 7]{frongillo2018elicitation} to bound the convex elicitation complexity of the Bayes risk of the loss.
\btw{Raf Note to self: need to sync the refs to the actual version on arxiv... or something...}
%\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
\begin{restatable}[\citep{ramaswamy2016convex}]{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
  Let $L$ elicit some $\Gamma:\simplex\to\reals^d$.
  Let $p\in\relint\simplex$ and let $\Gamma_r$ be some level set of $\Gamma$ such that
  (i) $p\in\Gamma_r$,
  (ii) $\codim(\affhull(\Gamma_r))=d$, and
  (iii) either $\Gamma_r$ is a singleton or $\lbar$ is nonconstant on $\Gamma_r$.
  Then $\eliccvx(\lbar) \geq \min(d+1,n-1)$.
\end{restatable}

@@

\subsection{Proof of Theorem~\ref{thm:bayes-risk-lower-bound}}

\bayesrisklowerbound
\begin{proof}
	Suppose that we have some convex loss $\hat L:\reals^k\times\Y\to\reals$ eliciting a property $\hat\Gamma:\simplex\to\reals^k$, and link $\psi : \reals^k \to \reals$ such that $\lbar = \psi \circ \hat\Gamma$.
	% The condition $\iden(\Gamma)=d$ implies the existence of some level set $\Gamma_r$ such that $\codim(\affhull(\Gamma_r)) \geq d$; otherwise, taking $F_r = \affhull(\Gamma_r)$ for all reports $r\in\reals^d$, we would have $\codim(F_r) \leq d-1$ and $\Gamma_r = F_r \cap \simplex$, implying $\iden(\Gamma)\leq d-1$.
	The proof of \citet[Theorem 4]{frongillo2018elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that every level set of $\hat\Gamma$ is contained in a level set of $\Gamma$; for completeness we give the argument here.
	Suppose for a contradiction that we have $p,p'$ with $\hat\Gamma(p)=\hat\Gamma(p')$ but $\Gamma(p) \neq \Gamma(p')$.
	As $\lbar = \psi \circ \hat\Gamma$, we also have $\lbar(p) = \lbar(p')$.
	Letting $p'' = \tfrac 1 2 p +  \tfrac 1 2 p'$, Lemma~\ref{lem:elic-complex-bayes-concave} would then give us $\lbar(p'') >  \tfrac 1 2 \lbar(p) +  \tfrac 1 2 \lbar(p') = \lbar(p)$.
	By \citet{osband1985providing}, the level sets $\hat\Gamma_{\hat r}$ are convex, giving $\hat\Gamma(p'') = \hat\Gamma(p)$, which would imply $\lbar(p'')=\lbar(p)$, contradicting $\lbar = \psi \circ \hat\Gamma$.
	We conclude $\hat\Gamma$ must refine $\Gamma$, and thus $\hat L$ actually indirectly elicits $\Gamma$ through some other link function.
	% The proof of \cite[Theorem 4]{frongillo2018elicitation} argues that $\hat\Gamma$ must refine $\Gamma$, in the sense that for all $\hat r \in \hat\Gamma(\simplex)$ we have $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ for some $r\in\reals^k$.
